Etox-Base: A tool to derive exposure endpoints from chemical test results

### 2019-02-05 article/article.tex

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage{natbib} % citations
\usepackage{csvsimple}
\usepackage{rotating} % to rotate tables
%% tikz packages
\usepackage{tikz}
\usepackage{forest}
\usetikzlibrary{trees, arrows, shapes.geometric, positioning}
\usepackage{standalone}
%% text packages
\usepackage{siunitx} % fake ° symbol \ang{}
\usepackage[super]{nth} % for 1st, 2nd etc. \nth{}
\usepackage{hyperref}

@@

\begin{table}
%\begin{sidewaystable}
    \csvautotabular[respect underscore=true]{data/scripts.csv}
    \caption{R Scripts to query and process data obtained from various resources. The script tree, i.e. the order which script is processed can be found in}
    \label{table:processing-scripts};
%\end{sidewaystable}
\end{table}

\csvreader[tabular=|l|l|,
    table head=\hline & category & description\\\hline,
    late after line=\\\hline]
{data/scripts.csv}{name=\category,surname=\description}
%{\thecsvrow & \surname~\name & \age}

>>>>

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage{natbib} % citations
\usepackage{csvsimple}
\usepackage{pgfplotstable}
\usepackage{rotating} % to rotate tables
%% tikz packages
\usepackage{tikz}
\usepackage{forest}
\usetikzlibrary{trees, arrows, shapes.geometric, positioning}
\usepackage{standalone}
%% text packages
\usepackage{siunitx} % fake ° symbol \ang{}
\usepackage[super]{nth} % for 1st, 2nd etc. \nth{}
\usepackage{hyperref}

@@

%\begin{table}
\begin{sidewaystable}
    \pgfplotstabletypeset[
    col sep=comma,
    string type,
    columns={Script,Description},
    columns/Description/.style={column type={|l}},
    columns/Script/.style={column type={|l}, % needed for replacing underscore
                           postproc cell content/.code={%
                                \pgfplotsutilstrreplace{_}{\_}{##1}%
                                \pgfkeyslet{/pgfplots/table/@cell content}\pgfplotsretval
                                },
                            },
    every head row/.style={before row=\hline,after row=\hline},
	every last row/.style={after row=\hline},
    ]{data/scripts.csv}
    \caption{R Scripts to query and process data obtained from various resources. The script tree, i.e. the order which script is processed can be found in}
    \label{table:processing-scripts};
\end{sidewaystable}
%\end{table}
